To Whom It May Concern,

I am writing to recommend Nguyen Hoang Nhat for admission to the VEF 2.0 Program. I am Dr. Nguyen Thi Ngoc Anh, a lecturer at the Faculty of Mathematics and Informatics at Hanoi University of Science and Technology (HUST). With 20 years of experience in statistics and data analysis, I have had the privilege of instructing numerous students, and Nhat stands out as an exceptional individual.

Nhat is a student in the talented program for Mathematics and Informatics at HUST. He consistently demonstrates a profound understanding of complex topics and an eagerness to apply them practically. I have had the pleasure of teaching Nhat in several courses, including "Stochastic Processes and their Applications" and "Time Series Analysis", where he has consistently excelled and earning grade A. His final project for "Stochastic Processes" was particularly impressive, where he used a different approach to solve a problem that had stumped his classmates. This project showcased his technical expertise, innovative thinking, and dedication to exceptional work.

Nhat's abilities extend beyond theoretical knowledge. Currently, we are collaborating on a government project focused on developing a system for verifying the legal authority of promulgated documents.  Nhat's  contribution to this project has been truly outstanding.  He proposed a novel method that achieved an impressive 94.11\% accuracy on a real-world dataset containing complex legal cases.  This solution has been successfully implemented into a product currently used by Vietnamese state agencies, significantly reducing their workload in legal document verification.  This project experience demonstrates Nhat's ability to apply his knowledge to solve real-world problems with tangible impact.

While still pursuing his studies, Nhat's impressive talent has already garnered him recognition in the industry. He was recently accepted as an AI Researcher intern specializing in Speech and Language Processing at the prestigious Samsung R&D Center Vietnam.  His internship has recently transitioned to a full-time staff position, further highlighting his valuable skills and dedication.

Nhat is not only a brilliant researcher but also a collaborative individual. During our research project, he consistently showcased excellent communication and problem-solving skills, effectively collaborating with me and other team members.

Nhat's exceptional academic performance, innovative research contributions, and experience in a leading industry research lab undeniably make him an outstanding candidate for your program.  His dedication, talent, and passion for AI research guarantee his valuable contributions to your program and the broader field. I wholeheartedly endorse his application and have no doubt he will thrive in your esteemed program.

Please do not hesitate to contact me at anh.nguyenthingoc@hust.edu.vn if you require any further information.

Sincerely,

Dr. Nguyen Thi Ngoc Anh

Nhat possesses a strong work ethic, intellectual curiosity, and a deep interest in Artificial Intelligence and Machine Learning, perfectly aligning with the VEF 2.0 program's focus on these areas. His eagerness to contribute extends beyond academics, evidenced by his impactful real-world project and industry recognition. I am confident that Nhat's exceptional talent, research experience, innovative spirit, and commitment to applying scientific knowledge to solve real-world problems make him an ideal candidate for the VEF 2.0 program. He will undoubtedly be a valuable asset to your program and contribute significantly to the advancement of science and technology in Vietnam.

I wholeheartedly recommend Nhat for the VEF 2.0 program. Please feel free to contact me at anh.nguyenthingoc@hust.edu.vn if you require any further information.

Sincerely,

Dr. Nguyen Thi Ngoc Anh